\Large {\bf rt1d: Documentation}

### 2012-05-01 doc/manual/rt1d_manual.tex
Added README file to root directory.
In the process of implementing cosmological expansion...not going so great.

%%% START custom commands
\newcommand{\HI}{\text{HI}}
\newcommand{\HII}{\text{HII}}
\newcommand{\HeI}{\text{HeI}}
\newcommand{\HeII}{\text{HeII}}
\newcommand{\HeIII}{\text{HeIII}}
\newcommand{\nH}{n_{\text{H}}} 
\newcommand{\nHI}{n_{\text{HI}}} 
\newcommand{\nHII}{n_{\text{HII}}}  
\newcommand{\nHe}{n_{\text{He}}}
\newcommand{\xHI}{x_{\text{HI}}} 
\newcommand{\xHII}{x_{\text{HII}}} 
\newcommand{\xHeI}{x_{\text{HeI}}} 
\newcommand{\xHeII}{x_{\text{HeII}}} 
\newcommand{\xHeIII}{x_{\text{HeIII}}}  
\newcommand{\nHeI}{n_{\text{HeI}}}
\newcommand{\nHeII}{n_{\text{HeII}}}
\newcommand{\nHeIII}{n_{\text{HeIII}}}  
\newcommand{\nel}{n_{\text{e}}}  
\newcommand{\ntot}{n_{\text{tot}}}
\newcommand{\nnu}{$n_{\nu}$}
\newcommand{\ncol}{N_i}
\newcommand{\gHI}{\Gamma_{\text{HI}}}  
\newcommand{\gHeI}{\Gamma_{\text{HeI}}}
\newcommand{\gHeII}{\Gamma_{\text{HeII}}}
\newcommand{\aHII}{\alpha_{\text{HII}}}  
\newcommand{\aHeII}{\alpha_{\text{HeII}}}  
\newcommand{\aHeIII}{\alpha_{\text{HeIII}}}
\newcommand{\bHI}{\beta_{\text{HI}}} 
\newcommand{\bHeI}{\beta_{\text{HeI}}}  
\newcommand{\bHeII}{\beta_{\text{HeII}}}  
\newcommand{\xiHeII}{\xi_{\text{HeII}}}
\newcommand{\kB}{k_{\text{B}}}
\newcommand{\fheat}{f^{\text{heat}}}
\newcommand{\fheatE}{f_{(\nu - \nu_i)}^{\text{heat}}}
\newcommand{\fion}{f_i^{\text{ion}}}
\newcommand{\fionE}{f_{ij,(\nu - \nu_j)}^{\text{ion}}}
\newcommand{\Lbol}{\mathcal{L}_{\text{bol}}}
\newcommand{\spec}{\mathcal{N}}
\newcommand{\Heat}{\mathcal{H}}
\newcommand{\trec}{$t_{\text{rec}}$}
\newcommand{\Lbox}{L_{\mathrm{box}}}
\newcommand{\dx}{\Delta x}
\newcommand{\dd}{\text{d}}
\newcommand{\Htwo}{\mathrm{H}_2}
\newcommand{\drIF}{$\Delta r_{\mathrm{IF}}$}
\newcommand{\dTb}{$\delta T_b$}
\newcommand{\Nvec}{\mathbf{N}}
\newcommand{\sh}{\mathrm{sh}}
%%% END custom commands

@@

@@

%%% 
%% Start to Finish
%%%
\section{Start to Finish}

>>>>

%%% START custom commands
\newcommand{\H}{\text{H}}
\newcommand{\He}{\text{He}}
\newcommand{\HI}{\text{HI}}
\newcommand{\HII}{\text{HII}}
\newcommand{\HeI}{\text{HeI}}
\newcommand{\HeII}{\text{HeII}}
\newcommand{\HeIII}{\text{HeIII}}
\newcommand{\nH}{n_{\text{H}}} 
\newcommand{\nHI}{n_{\text{HI}}} 
\newcommand{\nHII}{n_{\text{HII}}}  
\newcommand{\nHe}{n_{\text{He}}}
\newcommand{\xHI}{x_{\text{HI}}} 
\newcommand{\xHII}{x_{\text{HII}}} 
\newcommand{\xHeI}{x_{\text{HeI}}} 
\newcommand{\xHeII}{x_{\text{HeII}}} 
\newcommand{\xHeIII}{x_{\text{HeIII}}}  
\newcommand{\nHeI}{n_{\text{HeI}}}
\newcommand{\nHeII}{n_{\text{HeII}}}
\newcommand{\nHeIII}{n_{\text{HeIII}}}  
\newcommand{\nel}{n_{\text{e}}}  
\newcommand{\ntot}{n_{\text{tot}}}
\newcommand{\nnu}{$n_{\nu}$}
\newcommand{\ncol}{N_i}
\newcommand{\gHI}{\Gamma_{\text{HI}}}  
\newcommand{\gHeI}{\Gamma_{\text{HeI}}}
\newcommand{\gHeII}{\Gamma_{\text{HeII}}}
\newcommand{\aHII}{\alpha_{\text{HII}}}  
\newcommand{\aHeII}{\alpha_{\text{HeII}}}  
\newcommand{\aHeIII}{\alpha_{\text{HeIII}}}
\newcommand{\bHI}{\beta_{\text{HI}}} 
\newcommand{\bHeI}{\beta_{\text{HeI}}}  
\newcommand{\bHeII}{\beta_{\text{HeII}}}  
\newcommand{\xiHeII}{\xi_{\text{HeII}}}
\newcommand{\kB}{k_{\text{B}}}
\newcommand{\fheat}{f^{\text{heat}}}
\newcommand{\fheatE}{f_{(\nu - \nu_i)}^{\text{heat}}}
\newcommand{\fion}{f_i^{\text{ion}}}
\newcommand{\fionE}{f_{ij,(\nu - \nu_j)}^{\text{ion}}}
\newcommand{\Lbol}{\mathcal{L}_{\text{bol}}}
\newcommand{\spec}{\mathcal{N}}
\newcommand{\Heat}{\mathcal{H}}
\newcommand{\trec}{$t_{\text{rec}}$}
\newcommand{\Lbox}{L_{\mathrm{box}}}
\newcommand{\dx}{\Delta x}
\newcommand{\dd}{\text{d}}
\newcommand{\Htwo}{\mathrm{H}_2}
\newcommand{\drIF}{$\Delta r_{\mathrm{IF}}$}
\newcommand{\dTb}{$\delta T_b$}
\newcommand{\Nvec}{\mathbf{N}}
\newcommand{\sh}{\mathrm{sh}}
%%% END custom commands

@@

% Cosmology
\subsection{Additional Complexity: Cosmological Expansion}
For an expanding universe, the number density of species $i$ (neglecting all processes except for the cosmological expansion) is
\begin{equation}
    n_i(z) = \bar{n}_i^0 (1 + z)^3 ,
\end{equation}    
where $\bar{n}_i^0$ is the number density today.  The rate of change in the number density of species $i$ is then
\begin{align}
    \frac{dn_i}{dt} & = 3 \bar{n}_i^0 (1 + z)^2 \frac{dz}{dt} \nonumber \\
    & = 3 \bar{n}_i^0 (1 + z)^3 H(z)
\end{align}
It will be advantageous to work with ionized fractions now, i.e.
\begin{align}
    \dot{x}_{\HII} & = (\gHI + \gamma_{\HI} + \bHI \nel) (1 - \xHII) - \aHII \nel \xHII   \label{eq:HIIRateEquation} \\ 
    \dot{x}_{\HeII} & = (\gHeI + \gamma_{\HeI} + \bHeI \nel) (1 - \xHeI - \xHeII) \nonumber + \aHeIII \nel \xHeIII \\  & - (\bHeII + \aHeII + \xiHeII) \nel \xHeII \label{eq:HeIIRateEquation} \\ 
    \dot{x}_{\HeIII} & = (\gHeII + \gamma_{\HeII} + \bHeII \nel) \xHeII  - \aHeIII \nel \xHeIII . \label{eq:HeIIIRateEquation}
\end{align}
where
\begin{equation}
    n_e = \bar{n}_{\H}^0 (1 + \xHII) (1 + z)^3 + \bar{n}_{\He}^0 (1 + \xHeII + 2 \xHeIII) (1 + z)^3
\end{equation}

@@
